\documentclass[letterpaper, 11pt]{article}
\usepackage[left=0.7in,top=0.75in,right=0.75in,bottom=0.7in]{geometry}
\begin{document}
\pagestyle{empty}
\noindent Md Shaifur Rahman\\
1147 N. Country Rd\\
Stony Brook, NY-11790\\
Cellphone: +1-631-949-6815\\
Email: mdshaifur.rahman@stonybrook.edu\\

\noindent Hello,

I am a second-year PhD student in the Computer
Science department in Stony Brook University, NY. 
Before starting my PhD in Stony Brook University, I earned my B.Sc. and M.Sc. in Computer 
Science from Bangladesh 
University of Engineering & Technology (BUET), the top engineering school in my home 
country Bangladesh. Later, I joined my Alma Mater as a lecturer and was subsequently 
promoted to the post of Assistant Professor before getting education leave to complete
 my PhD. 

 
 I had the privilege to work with the brightest minds of my country both as a
  teacher and a student in BUET. As an instructor, I took undergrad courses like Object
   Orient Programming (C++, Java), Database Systems (Oracle, MySQL), Operating Systems 
   (Shell scripting, NACHOS), VLSI Design (Verilog,
   PSPICE) and so on.
   I taught my students the most up-to-date curriculum, prepared challenging problems for
    lab sessions and exams; and
     supervised a lot of student projects. 
       
       
       %I was exposed to the vast computational complexity related to
       %fabrications through my M.Sc. course titled 'VLSI Layout Algorithms'
       %which entailed topics like multi-layer channel routing,
       %graph-theoretic formulations and optimizations etc. 
       As a faculty of the
       premium technology school, I also had the opportunity to be on the consultancy 
       teams dealing with major IT issues in my country for example, vetting the newly 
       installed data centers in the Central Bank in Bangladesh, preparing spec for the 
       first ever machine readable passport project in Bangladesh etc. This experiences 
       honed my insight into many 
       large-scale implementation issues of software or solutions in the real world. 
       
       
After joining Stony Brook University, I took recitation classes as a
Teaching Assistant for undergrad courses like Software Engineering, Theory of
Database Systems etc.
 I also just completed my PhD ''breadth'' course requirements last fall
semester and preparing for my research proposal this semester. Many of these course works 
involved extensive term projects with significant coding effort. Some of these have 
been detailed in my resume.
My current research area includes high speed wireless backbone in Cellular Networks 
and Data Centers, Free Space Optics (FSO), algorithmic issues related to the
deployment of base stations, traffic engineering in the heterogeneous networks
etc. My advisor Prof. Himanshu Gupta's ongoing research in FSO
in Data Centers resulted in a publication in SIGCOMM-2014. As his new PhD student, 
I am researching in using short-link
switchable FSO in wireless back-hauls for metro area small-cell cellular
networks.

I believe I have a strong communication and interpersonal management skills
after all these years of teaching. I also have the exposure to both classroom pedagogy and practical
issues related to both real-world software and hardware solutions. One of the
requirements of my PhD curriculum is the industrial experiences via internships.
Therefore, I am seeking internship positions related to my skills for
Summer-2015. I am looking forward to hearing from you if you think that my
background/experience could be a match for your ongoing projects or research.\\
\\
\\
\\
Sincerely,\\ 
\textit{Md Shaifur Rahman}\\ 
PhD Student\\
Department of Computer Science\\
Stony Brook University, NY 11794-4400.\\
\end{document}

